\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-06-25 write_up/Process_model.tex
Text updates and reworking plots

% -------------------------------------------------
% A last flourish which breaks all the rules
\draw [->,purple, dotted, thick, shorten >=1mm]
  (p3.south) -- ++(5mm,-3mm)  -- ++(87mm,0mm) 
  |- node [black, near end, yshift=1.75em, it]
    {} ($(p1.north) + (0,0.3)$);
% -------------------------------------------------
\end{tikzpicture}
\caption{Overview Schematic of simulation model. The blue boxes indicate fleet
	dynamics processes, the green boxes population dynamics processes while
	the white boxes are the time steps at which processes occur; $t$ = tow,
	$tmax$ is the total number of tows; (Rec), (Pop Movement), (Pop
	Dynamics) logic gates for recruitment periods, population movement and
	population dynamics for each of the populations, (Past Knowledge) a
	switch whether to use a random (exploratory) or past knowledge
	(exploitation) fishing strategy.}
%%\label{fig:overview}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% -------------------------------------------------
% A last flourish which breaks all the rules
\draw [->,purple, dotted, thick, shorten >=1mm]
  (p3.south) -- ++(5mm,-3mm)  -- ++(87mm,0mm) 
  |- node [black, near end, yshift=1.75em, it]
    {} ($(p1.north) + (0,0.3)$);
% -------------------------------------------------
\end{tikzpicture}
\caption{Schematic overview of the simulation model. Blue boxes indicate fleet
	dynamics processes, the green boxes population dynamics processes while
	the white boxes are the time steps at which processes occur; $t$ = tow,
	$tmax$ is the total number of tows; (Rec), (Pop Movement), (Pop
	Dynamics) logic gates for recruitment periods, population movement and
	population dynamics for each of the populations, (Past Knowledge) a
	switch whether to use a random (exploratory) or past knowledge
	(exploitation) fishing strategy.}
%%\label{fig:overview}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%
